STA610 Case Study 1 Team 4 Report

### 2021-03-22 final_report.Rmd

* dose_per_mg: Controlling for other variables, for every one milligram increase of dosage, the price per mg of oxymorphone increases by a multiplicative effect of exp(-0.0151868) = 0.9849279, about a 1.51% reduction.

* bulk_purchase: “Not bulk purchase” is the reference group.
  * Controlling for other variables, bulk purchase reduces the price per mg of oxymorphone by a multiplicative effect of exp(-0.1691121) = 0.8444142, about a 15.56% reduction.

* source: “Source: Unknown” is the reference group. 
  * Controlling for other variables, purchasing oxymorphone with Internet source tends to increase the price per mg by a multiplicative effect of exp(0.1339468) = 1.143332, about a 14.33% increase than the price per mg of oxymorphone for people with unknown drug source.
  * Controlling for other variables, purchasing oxymorphone with Internet Pharmacy source tends to reduce the price per mg by a multiplicative effect of exp(-0.4584378) = 0.6322706, about a 36.77% reduction than the price per mg of oxymorphone for people with unknown drug source.
  * Controlling for other variables, purchasing oxymorphone with personal source tends to increase the price per mg by a multiplicative effect of exp(0.0565153) = 1.058143, about a 5.81% increase than the price per mg of oxymorphone for people with unknown drug source.
  * Controlling for other variables, purchasing oxymorphone with “heard it” source tends to increase the price per mg by a multiplicative effect of exp(0.1790027) = 1.196024, about a 19.6% increase than the price per mg of oxymorphone for people with unknown drug source.

* Primary Reason: “Primary_Reason: Blank” is the reference group. 
  * Controlling for other variables, purchasing oxymorphone with primary reason Left unanswered tends to increase the price per mg by a multiplicative effect of exp(0.0176846) = 1.017842, about a 1.78% increase than the price per mg of oxymorphone for people with Blank primary reason.
  * Controlling for other variables, purchasing oxymorphone with primary reason Other or unknown tends to increase the price per mg by a multiplicative effect of exp(0.0486307) = 1.049833, about a 4.98% increase than the price per mg of oxymorphone for people with Blank primary reason.
  * Controlling for other variables, purchasing oxymorphone with primary reason Self-treat tends to increase the price per mg by a multiplicative effect of exp(0.1034974) = 1.109043, about a 10.9% increase than the price per mg of oxymorphone for people with Blank primary reason.
  * Controlling for other variables, purchasing oxymorphone with primary reason Enjoyment tends to increase the price per mg by a multiplicative effect of exp(0.1838890) = 1.201882, about a 20.19% increase than the price per mg of oxymorphone for people with Blank primary reason.
  * Controlling for other variables, purchasing oxymorphone with primary reason Resell tends to reduce the price per mg by a multiplicative effect of exp(-0.3179197) = 0.7276612, about a 27.23% reduction than the price per mg of oxymorphone for people with Blank primary reason.
  * Controlling for other variables, purchasing oxymorphone with primary reason Refuse to answer tends to increase the price per mg by a multiplicative effect of exp(0.0564516) = 1.058075, about a 5.81% increase than the price per mg of oxymorphone for people with Blank primary reason.

>>>>

* *dose_per_mg*: Controlling for other variables, for every one milligram increase of dosage, the price per mg of oxymorphone increases by a multiplicative effect of exp(-0.0151868) = 0.9849279, about a 1.51% reduction.

* *bulk_purchase* ("not bulk purchase" is the reference): Controlling for other variables, bulk purchase reduces the price per mg of oxymorphone by a multiplicative effect of exp(-0.1691121) = 0.8444142, about a 15.56% reduction.

* *source* (“Source: Unknown” is the reference, other levels ommitted for brevity):
    + Controlling for other variables, purchasing oxymorphone with Internet source tends to increase the price per mg by a multiplicative effect of exp(0.1339468) = 1.143332, about a 14.33% increase than the price per mg of oxymorphone for people with unknown drug source.

* *Primary Reason* ("Blank" is the reference, other levels omitted for brevity):
    + Controlling for other variables, purchasing oxymorphone with primary reason Self-treat tends to increase the price per mg by a multiplicative effect of exp(0.1034974) = 1.109043, about a 10.9% increase than the price per mg of oxymorphone for people with Blank primary reason.
